### 2021-04-14 paper/ase21/eval.tex
[ASE21] temporal dump

\begin{itemize}
  \item RQ1: Quality of $\tool$: Performance / Precision
  \item RQ2: Survey of true bugs: TTL / creater or solver / \# by kinds
  \item RQ3: How many $\tool$ detect new bugs in the recent version? - detailed
    explanation
\end{itemize}

>>>>

We implemented $\tool$ in Scala by extending $\jiset$, a JavaScript IR-based
semantics extraction toolchain, with a worklist-based fixpoint algorithm for
type analysis.  Since $\jiset$ cannot automatically compiles algorithm steps
having uncommon writing styles to $\ires$ instructions, our tool reports
type-related specification bugs detected in fully compiled abstract algorithms.
For built-in libraries, we only targeted essential algorithms for
\jscode{Array}, \jscode{Object}, \jscode{Function}, \jscode{Math},
\jscode{Proxy}, and primitive types.  To evaluate $\tool$, we answer the
following research questions:
\begin{itemize}
  \item RQ1. \textbf{(Performance)} How long does $\tool$ take to perform type
    analysis for JavaScript specifications?
  \item RQ2. \textbf{(Precision)} How many type-related specification bugs
    detcted by $\tool$ are true bugs?
  \item RQ3. \textbf{(Effect of Refinement)} What is the effect of
    condition-based refinement for type analysis?
  \item RQ4: \textbf{(Survey of Detected Bugs)} What kind of properties true
    bugs detected by $\tool$ have?
\end{itemize}
The draft of the next version of ECMAScript (ES12, 2021) is fixed on March 9,
2021.  Thus, we targeted all different \inred{XXX} versions existed in the
official ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for
the recent three years from January 1, 2018 to March 9, 2021.  We performed our
experiments on five Ubuntu machines equipped with 4.2GHz Quad-Core Intel Core i7
and 32GB of RAM.

\subsection{Performance}

\todo: extract / type analysis / refinement

\subsection{Precision}

\todo: precision / refinement

\subsection{Survey of Detected Bugs}

\todo: TTL / creater or solver / \# by kinds / new bugs

### 2021-04-14 paper/ase21/intro.tex
[ASE21] temporal dump

% TODO: links in footnote
Unfortunately, there is no existing tool to automatically detect bugs in the
rapidly evolved JavaScript specifications.  Thus, the committee of ECMAScript
have tried to resolve this problem using additional annotations in abstract
algorithms.  Additional annotations make the specification more readable and
also they are useful for the specification-based tools such as JavaScript
engines~\cite{v8, graaljs, qjs, moddable}, static analyzers~\cite{safe, tajs,
jsai, wala}, and verification tools~\cite{javert}.  Thus, they decided to
manually insert two different annotations: 1) \textit{assertions} to denotes the
assumptions in a certain point of abstract algorithms, and 2) two different
\textit{prefixes} $\code{?}$ and $\code{!}$ to represent whether completion
records might be abrupt or not.  For example, ``Assert: Type(\textit{O}) is
Object'' denotes that the variable $\textit{O}$ always has an Object value at
this point and ``? \textbf{GetV}(\textit{V}, \textit{P})'' denotes that return
values of \textbf{GetV}(\textit{V}, \textit{P}) might be abrupt completions.
Moreover, they recently started the internal discussion of manual type
annotations for variables, parameters, and return values for each abstract
algorithm~\footnote{https://github.com/tc39/ecma262/pull/545\#issuecomment-559292107}.
However, to manually annotate types for all of them without any automated tool
is also labor-intensive and error-prone.  Furthermore, even though the such
manual type annotations can give more information for manual checking of
specification updates, it still does not provide any automatic approach to
detect specification bugs.

>>>>

% TODO: links in footnote
Unfortunately, there is no existing tool to automatically detect bugs in the
rapidly evolved JavaScript specifications.  Thus, the committee of ECMAScript
have tried to resolve this problem using additional annotations in abstract
algorithms.  Additional annotations make the specification more readable and
also they are useful for the specification-based tools such as JavaScript
engines~\cite{v8, graaljs, qjs, moddable}, debuggers~\cite{jsexplain}, static
analyzers~\cite{safe, tajs, jsai, wala}, and verification tools~\cite{javert}.
Thus, they decided to manually insert two different annotations: 1)
\textit{assertions} to denotes the assumptions in a certain point of abstract
algorithms, and 2) two different \textit{prefixes} $\code{?}$ and $\code{!}$ to
represent whether completion records might be abrupt or not.  For example,
``Assert: Type(\textit{O}) is Object'' denotes that the variable $\textit{O}$
always has an Object value at this point and ``? \textbf{GetV}(\textit{V},
\textit{P})'' denotes that return values of \textbf{GetV}(\textit{V},
\textit{P}) might be abrupt completions.  Moreover, they recently started the
internal discussion of manual type annotations for variables, parameters, and
return values for each abstract
algorithm~\footnote{https://github.com/tc39/ecma262/pull/545\#issuecomment-559292107}.
However, to manually annotate types for all of them without any automated tool
is also labor-intensive and error-prone.  Furthermore, even though the such
manual type annotations can give more information for manual checking of
specification updates, it still does not provide any automatic approach to
detect specification bugs.

### 2021-04-14 paper/ase21/related.tex
[ASE21] temporal dump

\begin{itemize}
  \item Abstract Interpretation~\cite{ai1977, ai1992}
  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
  \item JavaScript Manual Mechanized Specification:
    \begin{itemize}
      \item The Essence of Javascript~\cite{lambdajs}
      \item A Trusted Mechanised JavaScript Specification~\cite{jscert}
      \item JaVerT: JavaScript Verification Toolchain~\cite{javert}
      \item KJS: A complete formal semantics of JavaScript~\cite{kjs}
      \item JSExplain: A Double Debugger for JavaScript~\cite{jsexplain}
      \item JEST: N+ 1-version Differential Testing of Both JavaScript Engines
        and Specification~\cite{jest}
    \end{itemize}
  \item Automatic Mechanized Specification for others:
    \begin{itemize}
      \item Automatic extraction of x86 formal semantics from its natural
        language description~\cite{x86}
      \item Formal semantics extraction from natural language specifications for
        ARM~\cite{arm}
      \item SpecTest: Specification-Based Compiler Testing~\cite{spectest}
      \item BASESPEC: Comparative Analysis of Baseband Software and Cellular
        Specifications for L3 Protocols~\cite{basespec}
    \end{itemize}
\end{itemize}

>>>>

\paragraph{ECMAScript-based Applications}
\begin{itemize}
  \item Engines~\cite{v8, graaljs, qjs, moddable}
  \item Static Analyzer~\cite{safe, tajs, jsai, wala}
  \item Debuggers: JSExplain: A Double Debugger for JavaScript~\cite{jsexplain}
  \item Verification Tool: JaVerT: JavaScript Verification
    Toolchain~\cite{javert}
\end{itemize}

\paragraph{Mechanized Specifications}
\begin{itemize}
  % manual
  \item The Essence of Javascript~\cite{lambdajs}
  \item A Trusted Mechanised JavaScript Specification~\cite{jscert}
  \item KJS: A complete formal semantics of JavaScript~\cite{kjs}

  % automatic
  \item BASESPEC: Comparative Analysis of Baseband Software and Cellular
    Specifications for L3 Protocols~\cite{basespec}
  \item Automatic extraction of x86 formal semantics from its natural
    language description~\cite{x86}
  \item Formal semantics extraction from natural language specifications for
    ARM~\cite{arm}
  \item SpecTest: Specification-Based Compiler Testing~\cite{spectest}
  \item Automatic Model Generation from Documentation for Java API Functions
  \item COMFORT: JS Fuzzer using ECMAScript
  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
\end{itemize}

\paragraph{Correctness of ECMAScript}
\begin{itemize}
  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
  \item JEST: N+1-version Differential Testing of Both JavaScript Engines
    and Specification~\cite{jest}
\end{itemize}

% \begin{itemize}
%   \item Abstract Interpretation~\cite{ai1977, ai1992}
%   \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
%   \item JavaScript Manual Mechanized Specification:
%     \begin{itemize}
%       \item The Essence of Javascript~\cite{lambdajs}
%       \item A Trusted Mechanised JavaScript Specification~\cite{jscert}
%       \item JaVerT: JavaScript Verification Toolchain~\cite{javert}
%       \item KJS: A complete formal semantics of JavaScript~\cite{kjs}
%       \item JEST: N+ 1-version Differential Testing of Both JavaScript Engines
%         and Specification~\cite{jest}
%     \end{itemize}
%   \item Automatic Mechanized Specification for others:
%     \begin{itemize}
%       \item Automatic extraction of x86 formal semantics from its natural
%         language description~\cite{x86}
%       \item Formal semantics extraction from natural language specifications for
%         ARM~\cite{arm}
%       \item SpecTest: Specification-Based Compiler Testing~\cite{spectest}
%       \item BASESPEC: Comparative Analysis of Baseband Software and Cellular
%         Specifications for L3 Protocols~\cite{basespec}
%     \end{itemize}
% \end{itemize}
